Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Added beginnings of a Challenges section.

>>>>

\section{Challenges}
\label{sec:challenges}

The challenges of introducing programmability into existing storage systems: (1) Programmability while keeping storage system available, (2) Finding and factoring out hard-wired policies and optimizations, (3) Bugs that were hidden because mechanisms were only exercised according to hard-wired policies and not in their full generality they were thought of -- programmability into a storage system turned out to be a great debugging tool.
